---
title: 'Module 12 Assignment'
author: "Kyle Johnstone"
date: "2025-04-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The Conversion Package

The premise of this package is to offer a mechanism for simple and easy conversions
for Americans. This package will include conversions for things such as money and measurements. The use of this package could be ideal for traveling or when working with foreign tools/equipment. 

## Money

Conversions for US Dollars into other currencies. The function will accept a dollar amount and convert it to the desired currency. 

```{r "money"}
# USD to Euro
to_euro <- function(dollars, rate = 0.88) {
  euro <- dollars * rate
  return(euro)
}
# USD to Yen
to_yen <- function(dollars, rate = 143.59) {
  yen <- dollars * rate
  return(yen)
}
# USD to CAD
to_canadian <- function(dollars, rate = 1.39) {
  canadian <- dollars * rate
  return(canadian)
}

```

## Weight

Conversions of pounds into common metric units. The function will accept a numerical value for pounds and convert it into the desired unit. 

```{r "weight"}
# Pounds to Grams
to_grams <- function(lbs, rate = 453.592) {
  grams <- lbs * rate
  return(grams)
}

to_kg <- function(lbs, rate = 0.453592) {
  kg <- lbs * rate
  return(kg)
}
```

## Temperature

Conversion from Fahrenheit to Celsius. The function will accept a numerical value for degrees Fahrenheit and convert it into Celsius. 

```{r "Temperature"}
# Fahrenheit to Celsius
to_C <- function(F) {
  C <- (F - 32) * (5/9)
  return(C)
}
```
